### 2022-05-17 manuscript.Rmd
Improve references

bibliography_main    : "manuscript_files/main.bib"
bibliography_methods : "manuscript_files/methods.bib"
csl                  : "manuscript_files/nature.csl"
citeproc             : false
link-citations       : yes

>>>>

bibliography_main    : "manuscript_files/main.bib"
bibliography_methods : "manuscript_files/methods.bib"
csl                  : "manuscript_files/nature.csl"
citeproc             : false
